Stream of Consciousness Literature: A 'Joyceless' Linguistic Landscape

### 2024-04-24 paper/paper.qmd
final paper updates

```{r}
#| echo: false
#| eval: true
#| label: tbl-joyce
#| tbl-cap: "An Examplary Table Containing Unprocessed Novel Text (James Joyce)"
#| warning: false

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-joyce-token
#| tbl-cap: Tokenized Stream of Consciousness Text (James Joyce)
#| warning: false
#| message: false

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-joyce-count
#| tbl-cap: Word Count after Tokenization (James Joyce)
#| warning: false
#| message: false

@@

\newpage
```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-count
#| layout-ncol: 2
#| fig-cap: "Comparative Analysis of Top 20 Word Frequencies from Famous SOC Authors"
#| fig-subcap: ["James Joyce", "Virginia Woolf", "Marcel Proust", "T.S. Eliot", "Katherine Mansfield"]

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-frequency
#| tbl-cap: "Word Frequency of Stream of Consciousness Novels, A Comparison Between Five Authors "
#| warning: false

>>>>

```{r}
#| echo: false
#| eval: true
#| label: tbl-joyce
#| tbl-cap: "Sample Table Containing Unprocessed Novel Text (James Joyce)"
#| warning: false

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-joyce-token
#| tbl-cap: Sample Table of Tokenized Stream of Consciousness Text (James Joyce)
#| warning: false
#| message: false

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-joyce-count
#| tbl-cap: Sample Table of Word Count after Tokenization (James Joyce)
#| warning: false
#| message: false

@@

\newpage
```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-count
#| layout-ncol: 2
#| fig-cap: "Comparative Analysis of Top 20 Word Count from Famous SOC Authors"
#| fig-subcap: ["James Joyce", "Virginia Woolf", "Marcel Proust", "T.S. Eliot", "Katherine Mansfield"]

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-frequency
#| tbl-cap: "Sample Table of Word Frequency in Stream of Consciousness Texts"
#| warning: false
